Publisher preprocessing summary

### 2021-03-04 inst/examples/publisher.Rmd
change

---
title: "Publisher preprocessing summary"
author: "`r author`"
date: "`r Sys.Date()`"
output: markdown_document
---

@@

 * `r length(which(df$self_published))` documents are identified as self-published (`r round(100*(length(which(df$self_published))/nrow(df)), 1)`%).

@@

### Publication timeline for top publishers

Title count

```{r top_pub_timeline, fig.height=10, fig.width=20, echo=FALSE}
# For some reason the ggplot never completes if top n > 2 ???
theme_set(theme_bw(20))
field <- "publisher"
tops <- names(top(df, field, n = 2))
dfs <- df %>% select(field, publication_decade) 
dfs$field <- as.character(dfs[[field]]); dfs[[field]] <- NULL
dfs <- dfs %>% filter(field %in% tops) %>%
               filter(!is.na(field) & !is.na(publication_decade)) %>%
	       count(field, publication_decade)
dfs$field <- as.factor(dfs$field)
p <- ggplot(dfs, aes(x = publication_decade, y = n, fill = field)) +
       geom_bar(stat = "identity", position = "stack", color = "black") +       
       labs(x = "Publication Decade", y = "Title Count",
            title = "Title count timeline for the top publishers") +
       scale_fill_grey() +
       guides(fill = guide_legend("Publisher")) 
# print(p)
```

@@

### Corporates

Summaries of the corporate field.

 * `r length(unique(df$corporate))` [unique corporates](output.tables/corporate_accepted.csv)

 * `r sum(!is.na(df$corporate))` documents have unambiguous corporate information (`r round(100*mean(!is.na(df$corporate)), 1)`%).

 * [Discarded corporate entries](output.tables/corporate_discarded.csv)

 * [Conversions from original to final names](output.tables/corporate_conversion_nontrivial.csv) (only non-trivial conversions shown)

The `r ntop` most common corporates are shown with the number of documents.

```{r summarycorporate2, echo=FALSE, message=FALSE, warning=FALSE, fig.width=12, fig.height=9}
p <- top_plot(df, "corporate", ntop)
p <- p + ggtitle(paste("Top corporates"))
p <- p + scale_y_log10()
p <- p + ylab("Documents")
print(p)
```

## Publisher

[Self-published accepted](https://github.com/COMHIS/fennica/blob/master/inst/examples/output.tables/self_published_accepted.csv) (Check for formatting and synonymes)

[Self-published raw fields](https://github.com/COMHIS/fennica/blob/master/inst/examples/output.tables/self_published_rawfields.csv) (Check that the self-publication is a correct classification for these docs)

## Corporate info

[Accepted corporate info](https://github.com/COMHIS/fennica/blob/master/inst/examples/output.tables/corporate_accepted.csv)

[Discarded corporate info](https://github.com/COMHIS/fennica/blob/master/inst/examples/output.tables/corporate_discarded.csv)

>>>>

---
title: "Publisher preprocessing summary"
author: "`r author`"
date: "`r Sys.Date()`"
output: md_document
---

@@

@@

@@
